---
title: "The PopuList Dashboard"
format: 
  dashboard:
    orientation: columns
    logo: images/logo.PNG
editor: visual
theme: cosmo
---

```{r}
#| message: FALSE
#| include: FALSE

# ==========================================================
# 1. SETUP: Load Packages and Data
# ==========================================================
library(tidyverse)
library(reactable)

populist <- read_csv2('/Users/lukefischer/Dropbox/The PopuList Repo/Data/The PopuList 3.0.csv')

# ==========================================================
# 2. DEFINITIONS: Date Formatting Functions
# ==========================================================

# Function to handle standard (non-borderline) date labeling
from_til_noborderline <- function(df, variable, start, end, start_nobl, end_nobl) {
  df |>
    mutate(
      {{variable}} := case_when(
        {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & {{end_nobl}} == 2100 ~ 
          paste0(as.character({{variable}}), " (", {{start_nobl}}, "-)"),
        {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & {{end_nobl}} != 2100 ~ 
          paste0(as.character({{variable}}), " (", {{start_nobl}}, "-", {{end_nobl}}, ")"),
        {{start}} == 1900 & {{end}} == 2100 & {{end_nobl}} != 2100 ~ 
          paste0(as.character({{variable}}), " (", "-", {{end_nobl}}, ")"),
        {{start}} == 1900 & {{end}} != 2100 & {{end_nobl}} == {{end}} ~ 
          paste0(as.character({{variable}}), " (", "-", {{end_nobl}}, ")"),
        {{start_nobl}} == 1900 & {{end_nobl}} != 2100 ~ 
          paste0(as.character({{variable}}), " (", "-", {{end_nobl}}, ")"),
        TRUE ~ as.character({{variable}})
      )
    )
}

# Function to handle borderline date labeling
from_til_borderline <- function(df, variable, start, end, start_nobl, end_nobl) {
  df |>
    mutate(
      {{variable}} := case_when(
        {{variable}} ==1 & {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & 
          {{end_nobl}} < {{end}} & {{end}} != 2100 ~ 
          paste0(as.character({{variable}})," (", {{end_nobl}}, "-", {{end}}, ")"), 
        {{variable}} ==1 & {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & 
          {{start}} < {{start_nobl}} & {{start}} != 1900 ~ 
          paste0(as.character({{variable}})," (",{{start}}, "-", {{start_nobl}}, ")"), 
        {{variable}} ==1 & {{start_nobl}} > {{start}} & 
          {{end}} == {{end_nobl}} & 
          {{start_nobl}} == 2100 & 
          {{start}} != 1900 ~ 
          paste0(as.character({{variable}})," (",{{start}}, "-)"), 
        {{variable}} ==1 & {{end_nobl}} < {{end}} & 
          {{start}} == {{start_nobl}} ~ 
          paste0(as.character({{variable}})," (",{{end_nobl}}, "-)"), 
        {{variable}} ==1 & {{start_nobl}} > {{start}} & 
          {{end}} == {{end_nobl}} & 
          {{end_nobl}} != 2100 ~ 
          paste0(as.character({{variable}})," (","-", {{start_nobl}}, ")"), 
        {{variable}} ==1 & {{start_nobl}} > {{start}} & 
          {{end}} == {{end_nobl}} & 
          {{end_nobl}} == 2100 & 
          {{start_nobl}} != {{end_nobl}}~ 
          paste0(as.character({{variable}})," (","-", {{start_nobl}}, ")"),
        TRUE ~ as.character({{variable}})
      )
    )
}

# ==========================================================
# 3. PROCESSING: Apply Date Functions to Ideologies
# ==========================================================

# Populism
populist <- from_til_noborderline(populist, populist, populist_start, populist_end, populist_startnobl, populist_endnobl) 
populist <- from_til_borderline(populist, populist_bl, populist_start, populist_end, populist_startnobl, populist_endnobl) 

# Far-right
populist <- from_til_noborderline(populist, farright, farright_start, farright_end, farright_startnobl, farright_endnobl) 
populist <- from_til_borderline(populist, farright_bl, farright_start, farright_end, farright_startnobl, farright_endnobl) 

# Far-left
populist <- from_til_noborderline(populist, farleft, farleft_start, farleft_end, farleft_startnobl, farleft_endnobl) 
populist <- from_til_borderline(populist, farleft_bl, farleft_start, farleft_end, farleft_startnobl, farleft_endnobl) 

# Euroskeptic
populist <- from_til_noborderline(populist, eurosceptic, eurosceptic_start, eurosceptic_end, eurosceptic_startnobl, eurosceptic_endnobl) 
populist <- from_til_borderline(populist, eurosceptic_bl, eurosceptic_start, eurosceptic_end, eurosceptic_startnobl, eurosceptic_endnobl) 

# ==========================================================
# 4. CLEANING: Selection and Manual Fixes
# ==========================================================

populist_cleaned <- populist |> 
  select(country_name, party_name, party_name_english, party_name_short, populist, populist_bl, farright, farright_bl, farleft, farleft_bl, eurosceptic, eurosceptic_bl, in_parliament) |> 
  mutate(populist = case_when(
    party_name_short == "FI1" ~ "1", 
    TRUE ~ populist
  ), 
  populist_bl = case_when(
    party_name_short == "FI1" ~ "1", 
    TRUE ~ populist_bl
  ), 
  eurosceptic_bl = case_when(
    party_name_short == "FI1" ~ "0", 
    party_name_short == "FI2" ~ "1", 
    TRUE ~ populist_bl
  )
  )

columns <- c("populist", "populist_bl", "farright", "farright_bl", "farleft", "farleft_bl", "eurosceptic", "eurosceptic_bl")

populist_cleaned <- populist_cleaned |>
  mutate(
    across(
      all_of(columns),
      ~ str_replace(.x, "^0 \\(", "1 (")
    )
  )

populist_cleaned <- populist_cleaned |>
  arrange(country_name, desc(in_parliament), party_name)

# ==========================================================
# 5. VISUALS: Replace Numeric Indicators with Symbols
# ==========================================================

populist_cleaned <- populist_cleaned |> 
  mutate(populist = str_replace(populist, "^1", "●"), 
         populist_bl = str_replace(populist_bl, "^1", "◐"), 
         farright = str_replace(farright, "^1", "●"), 
         farright_bl = str_replace(farright_bl, "^1", "◐"), 
         farleft = str_replace(farleft, "^1", "●"), 
         farleft_bl = str_replace(farleft_bl, "^1", "◐"), 
         eurosceptic = str_replace(eurosceptic, "^1", "●"), 
         eurosceptic_bl = str_replace(eurosceptic, "^1", "◐"), 
         in_parliament = str_replace(in_parliament, "^1", "●"), 
         populist = str_replace(populist, "^0", ""), 
         populist_bl = str_replace(populist_bl, "^0", ""), 
         farright = str_replace(farright, "^0", ""), 
         farright_bl = str_replace(farright_bl, "^0", ""), 
         farleft = str_replace(farleft, "^0", ""), 
         farleft_bl = str_replace(farleft_bl, "^0", ""), 
         eurosceptic = str_replace(eurosceptic, "^0", ""), 
         eurosceptic_bl = str_replace(eurosceptic, "^0", ""), 
         in_parliament = str_replace(in_parliament, "^0", "")) 

# ==========================================================
# 6. FINAL TABLE FORMATTING: Merging and Renaming
# ==========================================================

# Helper function to merge borderline and non-borderline columns for display
clean_table <- function(df, variable, variable_bl) {
  df |> 
    mutate(
      {{variable}} := case_when(
        str_detect({{variable}}, "^●$") & str_detect({{variable_bl}}, "^◐$") ~ {{variable_bl}},
        str_detect({{variable}}, "^●$") & str_detect({{variable_bl}}, "^◐ \\(") ~ {{variable_bl}},
        str_detect({{variable}}, "^● \\(") & str_detect({{variable_bl}}, "^◐ \\(") ~ paste0({{variable}}, "<br>", {{variable_bl}}),
        TRUE ~ {{variable}}
      )
    ) |> 
    select(!{{variable_bl}})
}

populist_cleaned <- clean_table(populist_cleaned, populist, populist_bl) 
populist_cleaned <- clean_table(populist_cleaned, farright, farright_bl) 
populist_cleaned <- clean_table(populist_cleaned, farleft, farleft_bl) 
populist_cleaned <- clean_table(populist_cleaned, eurosceptic, eurosceptic_bl) 

# Final column naming
names <- c("Country", "Party Name", "Name En.", "Abbr.", "Populist", "Far-Right", "Far-Left", "Euroskeptic", "In Parliament")
colnames(populist_cleaned) <- names

populist_cleaned <- populist_cleaned |> 
  relocate("Far-Left", .before = "Far-Right")

```

# General Overview

::: {.card title="**Party Information Per Country**"}

```{r}
#| echo: FALSE

reactable(
  populist_cleaned,
  groupBy = "Country",
  columns = list(
    "Populist" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#f0f5f9")),
    "Far-Right" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#f0f5f9")),
    "Far-Left" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#f0f5f9")),
    "Euroskeptic" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#f0f5f9")),
    "In Parliament" = 
      colDef(html = TRUE, width = 150, headerStyle = list(backgroundColor = "#f0f5f9")),
    "Abbr." = 
      colDef(html = TRUE, width = 120, headerStyle = list(backgroundColor = "#f0f5f9")),
    "Party Name" = 
      colDef(headerStyle = list(backgroundColor = "#f0f5f9")),
    "Name En." = 
      colDef(headerStyle = list(backgroundColor = "#f0f5f9")),
    "Country" = 
      colDef(
        width = 140,
        headerStyle = list(backgroundColor = "#f0f5f9"),
      grouped = JS("function(cellInfo) {
        return cellInfo.value
      }")
    )),
  highlight = TRUE,
  sortable = TRUE,
  defaultExpanded = FALSE,
  defaultPageSize = 6,
  searchable = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(
      fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
    searchInputStyle = list(width = "100%")
  )
)
```
::: 

# Further Explanation

## Column {width="25%"}

::: {.card title="**General Information**"}
The list under "General Overview" indicates whether or not a party is populist, far-right, far-left, eurosceptic, and currently in parliament. The table makes use of the following symbols:

|  Party | Vote-Share (%)  |
|---|---:|
| ●  | Party fulfills a characteristic |  
| ◐  | Party is a borderline case  |  
| ()  | Time interval  |  

For country specific reports, click on a country on the interactive map.
:::


## Column {width="75%"}

::: {.card title="**Country-Report Directory**"}

```{r}
# ==========================================================
# 1. LOAD PACKAGES AND SPATIAL DATA
# ==========================================================
library(eurostat)
library(sf)
library(tidyverse)
library(ggplot2)
library(ggiraph)

# Fetch European geospatial data (NUTS 0 - Country Level)
european <- get_eurostat_geospatial(resolution = 20, 
                                    nuts_level = 0, 
                                    year = 2016)

european <- european |> 
  select(id, geometry)

view(european)

# ==========================================================
# 2. DATA PREPARATION: Populist Votes
# ==========================================================
P <- read_csv("/Users/lukefischer/Dropbox/The PopuList Repo/Data/P.csv")

populist_votes <- P |> 
  filter(year == 2022) |> 
  select(country, c2_populist_votes) 

# Map country names to Eurostat ID codes
populist_votes <- populist_votes |> mutate(
  id = case_when(
    country == "Austria" ~ "AT",
    country == "Belgium" ~ "BE",
    country == "Bulgaria" ~ "BG",
    country == "Croatia" ~ "HR",
    country == "Cyprus" ~ "CY",
    country == "Czech_Republic" ~ "CZ",
    country == "Denmark" ~ "DK",
    country == "Estonia" ~ "EE",
    country == "Finland" ~ "FI",
    country == "France" ~ "FR",
    country == "Germany" ~ "DE",
    country == "Greece" ~ "GR",
    country == "Hungary" ~ "HU",
    country == "Iceland" ~ "IS",
    country == "Ireland" ~ "IE",
    country == "Italy" ~ "IT",
    country == "Latvia" ~ "LV",
    country == "Lithuania" ~ "LT",
    country == "Luxembourg" ~ "LU",
    country == "Netherlands" ~ "NL",
    country == "Norway" ~ "NO",
    country == "Poland" ~ "PL",
    country == "Portugal" ~ "PT",
    country == "Romania" ~ "RO",
    country == "Slovakia" ~ "SK",
    country == "Slovenia" ~ "SI",
    country == "Spain" ~ "ES",
    country == "Sweden" ~ "SE",
    country == "Switzerland" ~ "CH",
    country == "United_Kingdom" ~ "UK",
    TRUE ~ NA_character_
  )
)

# Join spatial data and clean names for display
populist_votes <- populist_votes |> 
  left_join(european)

populist_votes <- populist_votes |> 
  mutate(country = case_when(
    country == "United_Kingdom" ~ "United Kingdom", 
    country == "Czech_Republic" ~ "Czech Republic", 
    TRUE ~ country
  ))

# ==========================================================
# 3. INTERACTIVE DIRECTORY LINKS
# ==========================================================
populist_votes$links <- rep("placeholder", 30)

countries <- P |> 
  distinct(country) |>
  mutate(country = case_when(
    country == "Czech_Republic" ~ "Czech Republic", 
    country == "United_Kingdom" ~ "United Kingdom", 
    TRUE ~ country)) |> 
  pull(country) |> 
  as.character()

populist_votes <- populist_votes |> 
  mutate(links = str_glue("https://popu-list.github.io/Countries/{country}.html")) 

# ==========================================================
# 4. DATA VISUALIZATION: ggplot2 and ggiraph
# ==========================================================

# Create the static map with interactive aesthetics
directory_map <- populist_votes |>
  ggplot(aes(geometry = geometry, 
             data_id = country, 
             tooltip = paste0(country), 
             onclick = paste0('window.open("', links , '")'))) +
  geom_sf_interactive(fill = "#6FB6F2") +
  coord_sf(
    xlim = c(-28, 35),
    ylim = c(32, 73),
    expand = FALSE
  ) +
  labs(title = "") +
  theme_void() +
  theme(aspect.ratio = 0.9, 
        legend.position = "top", 
        legend.margin = margin(t = -20, r = 0, b = -30, l = 0),
        legend.title = element_text(hjust = 0.5, face = "bold", size = 8),
        legend.title.position = "top",
        legend.key.width = unit(0.8, "cm"), 
        legend.key.height = unit(0.3, "cm"))

# Render the interactive Girafe object
girafe(
  directory_map,
  width_svg = 5.5,
  height_svg = 5.5,
  options = list(
    opts_hover(css = "fill:#af69ee;"),
    opts_hover_inv(css = "opacity:0.3;"),
    opts_selection(type = "multiple", css = "fill:#FF851B;stroke:black;"),
    opts_tooltip(
      css = "background-color:black;color:black;padding:10px;border-radius:10px;box-shadow:10px 10px 10px rgba(0,0,0,0.3);font-family:Arial;font-size:15px;",
      opacity = 0.9,
      use_fill = TRUE
    ),
    opts_sizing(rescale = FALSE)
  ))
```
:::