---
title: "The PopuList Country-Report"
format: 
  dashboard:
    logo: images/logo.PNG
editor: visual
theme: lux
---

```{r}
#| include: FALSE

library(tidyverse)
library(gt)
library(reactable)

setwd("/Users/lukefischer/Dropbox/The PopuList/")

populist <- read_csv2("Data/The PopuList 3.0.csv")


from_til_noborderline <- function(df, variable, start, end, start_nobl, end_nobl) {
  df |>
    mutate(
      {{variable}} := case_when(
        {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & {{end_nobl}} == 2100 ~ 
          paste0(as.character({{variable}}), " (", {{start_nobl}}, "-)"),
        {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & {{end_nobl}} != 2100 ~ 
          paste0(as.character({{variable}}), " (", {{start_nobl}}, "-", {{end_nobl}}, ")"),
        {{start}} == 1900 & {{end}} == 2100 & {{end_nobl}} != 2100 ~ 
          paste0(as.character({{variable}}), " (", "-", {{end_nobl}}, ")"),
        TRUE ~ as.character({{variable}})
      )
    )
}

from_til_borderline <- function(df, variable, start, end, start_nobl, end_nobl) {
  df |>
    mutate(
      {{variable}} := case_when(
        {{variable}} ==1 & {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & 
          {{end_nobl}} < {{end}} & {{end}} != 2100 ~ 
          paste0(as.character({{variable}})," (", {{end_nobl}}, "-", {{end}}, ")"), 
        {{variable}} ==1 & {{start_nobl}} != 1900 & {{start_nobl}} != 2100 & 
          {{start}} < {{start_nobl}} & {{start}} != 1900 ~ 
          paste0(as.character({{variable}})," (",{{start}}, "-", {{start_nobl}}, ")"), 
        {{variable}} ==1 & {{start_nobl}} > {{start}} & 
          {{end}} == {{end_nobl}} & 
          {{start_nobl}} == 2100 & 
          {{start}} != 1900 ~ 
          paste0(as.character({{variable}})," (",{{start}}, "-)"), 
        {{variable}} ==1 & {{end_nobl}} < {{end}} & 
          {{start}} == {{start_nobl}} ~ 
          paste0(as.character({{variable}})," (",{{end_nobl}}, "-)"), 
        {{variable}} ==1 & {{start_nobl}} > {{start}} & 
          {{end}} == {{end_nobl}} & 
          {{end_nobl}} != 2100 ~ 
          paste0(as.character({{variable}})," (","-", {{start_nobl}}, ")"), 
        {{variable}} ==1 & {{start_nobl}} > {{start}} & 
          {{end}} == {{end_nobl}} & 
          {{end_nobl}} == 2100 &
          {{start_nobl}} != {{end_nobl}}~ 
          paste0(as.character({{variable}})," (","-", {{start_nobl}}, ")"),
        TRUE ~ as.character({{variable}})
      )
    )
}


# Populism
populist <- from_til_noborderline(populist, populist, populist_start, populist_end, populist_startnobl, populist_endnobl) 

populist <- from_til_borderline(populist, populist_bl, populist_start, populist_end, populist_startnobl, populist_endnobl) 

# farright
populist <- from_til_noborderline(populist, farright, farright_start, farright_end, farright_startnobl, farright_endnobl) 

populist <- from_til_borderline(populist, farright_bl, farright_start, farright_end, farright_startnobl, farright_endnobl) 

# farleft
populist <- from_til_noborderline(populist, farleft, farleft_start, farleft_end, farleft_startnobl, farleft_endnobl) 

populist <- from_til_borderline(populist, farleft_bl, farleft_start, farleft_end, farleft_startnobl, farleft_endnobl) 

# Euroskeptic
populist <- from_til_noborderline(populist, eurosceptic, eurosceptic_start, eurosceptic_end, eurosceptic_startnobl, eurosceptic_endnobl) 

populist <- from_til_borderline(populist, eurosceptic_bl, eurosceptic_start, eurosceptic_end, eurosceptic_startnobl, eurosceptic_endnobl) 


populist_cleaned <- populist |> 
  select(country_name, party_name, party_name_english, party_name_short, populist, populist_bl, farright, farright_bl, farleft, farleft_bl, eurosceptic, eurosceptic_bl, in_parliament) |> 
  mutate(populist = case_when(
            party_name_short == "FI1" ~ "1", 
            TRUE ~ populist
          ), 
          populist_bl = case_when(
            party_name_short == "FI1" ~ "1", 
            TRUE ~ populist_bl
          ), 
          eurosceptic_bl = case_when(
            party_name_short == "FI1" ~ "0", 
            party_name_short == "FI2" ~ "1", 
            
            TRUE ~ populist_bl
          )
        )


populist_cleaned <- populist_cleaned |> 
  mutate(populist = str_replace(populist, "^1", "●"), 
         populist_bl = str_replace(populist_bl, "^1", "◐"), 
         farright = str_replace(farright, "^1", "●"), 
         farright_bl = str_replace(farright_bl, "^1", "◐"), 
         farleft = str_replace(farleft, "^1", "●"), 
         farleft_bl = str_replace(farleft_bl, "^1", "◐"), 
         eurosceptic = str_replace(eurosceptic, "^1", "●"), 
         eurosceptic_bl = str_replace(eurosceptic, "^1", "◐"), 
         in_parliament = str_replace(in_parliament, "^1", "●"), 
         populist = str_replace(populist, "^0", ""), 
         populist_bl = str_replace(populist_bl, "^0", ""), 
         farright = str_replace(farright, "^0", ""), 
         farright_bl = str_replace(farright_bl, "^0", ""), 
         farleft = str_replace(farleft, "^0", ""), 
         farleft_bl = str_replace(farleft_bl, "^0", ""), 
         eurosceptic = str_replace(eurosceptic, "^0", ""), 
         eurosceptic_bl = str_replace(eurosceptic, "^0", ""), 
         in_parliament = str_replace(in_parliament, "^0", "")) 





clean_table <- function(df, variable, variable_bl) {
  
  df |> 
    mutate(
    {{variable}} := case_when(
      str_detect({{variable}}, "^●$") & str_detect({{variable_bl}}, "^◐$") ~ {{variable_bl}},
      str_detect({{variable}}, "^●$") & str_detect({{variable_bl}}, "^◐ \\(") ~ {{variable_bl}},
      str_detect({{variable}}, "^● \\(") & str_detect({{variable_bl}}, "^◐ \\(") ~ paste0({{variable}}, "<br>", {{variable_bl}}),
      TRUE ~ {{variable}}
    )
    ) |> 
      select(!{{variable_bl}})
}



populist_cleaned <- clean_table(populist_cleaned,populist,  populist_bl) 
populist_cleaned <- clean_table(populist_cleaned,farright,  farright_bl) 
populist_cleaned <- clean_table(populist_cleaned,farleft,  farleft_bl) 
populist_cleaned <- clean_table(populist_cleaned,eurosceptic,  eurosceptic_bl) 


library(gt)

names <- c("Country", "Party Name", "Party Name En.", "Abbr.", "Populist", "Far-Right", "Far-Left", "Euroskeptic", "In Parliament")

colnames(populist_cleaned) <- names

```

# General Overview

## Row {height="20%"}

::: {.card title="Symbol Explanation"}
This dashboard summarizes whether a party of country on the PopuList is populist, far-right, far-left, eurosceptic, and in parliament. The following symbols are used. Please refer to the main website for additional information.

-   A ● indicates that a party fulfills a characteristic
-   A ◐ indicates a borderline case
-   At times, the specific time intervals for when the characteristic was fulfilled is provided in parentheses

:::


## Row {height="80%"}

```{r}
#| echo: FALSE
#| title: Per Country Party Information


reactable(
  populist_cleaned,
  groupBy = "Country",
  columns = list(
    "Populist" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#daf0ff")),
    "Far-Right" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#daf0ff")),
    "Far-Left" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#daf0ff")),
    "Euroskeptic" = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#daf0ff")),
    "In Parliament" = 
      colDef(html = TRUE, width = 150, headerStyle = list(backgroundColor = "#daf0ff")),
    "Abbr." = 
      colDef(html = TRUE, width = 140, headerStyle = list(backgroundColor = "#daf0ff")),
    "Party Name" = 
      colDef(headerStyle = list(backgroundColor = "#daf0ff")),
    "Party Name En." = 
      colDef(headerStyle = list(backgroundColor = "#daf0ff")),
    "Country" = 
      colDef(
        headerStyle = list(backgroundColor = "#daf0ff"),
      grouped = JS("function(cellInfo) {
        return cellInfo.value
      }")
    )),
  highlight = TRUE,
  sortable = TRUE,
  defaultExpanded = FALSE,
  searchable = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(
      fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
    searchInputStyle = list(width = "100%")
  )
)
```
